Proposed Solution

### 2016-11-12 Ennan-Proposal/prelim.tex
stuff

\item ConfigC works on the premise that training dataset consists only 
of correct files, which is hard to achieve in practice. In the 
prototype we manually checked every file in the prototype. Clearly, this approach will not scale and  since 
  it is difficult for administrators or users to offer a
  set of 100\% correct configuration files for training.

\item The language model of ConfigC is still a starting point. It
  is hard to formulate a uniform representation for diverse
  configuration files.\ennan{we still need to put one more sentence
  here to distinguish why our current language model is better
  than ConfigC's language model}

\item ConfigC can only offer coarse-grained value correlation errors,
  \eg, $\texttt{max\_connections} > \texttt{mysql.max\_persistent}$.
  In practice, many software outages were caused by more tricky, called
  fine-grained value correlation~\cite{correlation}. For example, 
  in a MySQL configuration file, $\texttt{key\_buffer\_size}$ should be 
  higher than $\texttt{max\_connections} \times 
  \texttt{sort\_buffer\_size}$~\cite{correlation};
  otherwise, the MySQL load will be very high.

\item ConfigC cannot check singular value anomalies. For example,
  a parameter relating to memory in MySQL configuration files is
  setted too large, exhausting the RAM and causing extreme slowness
  or even a crash. Such an anomalous value does not violate any
  constraints (\eg, type error and value ordering error), but 
  it makes system behave wrongly.

@@

This proposal aims to address the above limitations.

>>>>

\item ConfigC works on the premise that the training dataset consists 
only of correct files, which is hard to achieve in practice. In the 
prototype we manually checked every file in the prototype. Clearly, this 
approach will not scale in practice. There exist a large set of 
real-world misconfigurations~\cite{configdataset}. Nevertheless, the 
errors are distributed through the files and do not all appear at the 
same spot. We believe that it should be possible to construct a correct
specification from the rules that hold in a significant majority of the 
files.

\item A language model used in ConfigC cannot handle a simple version of 
the {\tt {if-then}} command that sometimes appears in some configuration
files (such as Apache HTTPD). We already pointed out some issues with 
parsing and possible wrong typing. We need to develop a more 
accurate model which will be a uniform representation for diverse
  configuration files.

\item ConfigC offers only a limited number of templates to to detect 
correlation errors on keywords. It can detect, for example, 
keyword comparisons, but in practice many software outages were 
caused by more complex correlations (also called
  fine-grained correlations~\cite{correlation}). As an illustration,
  ConfigC cannot find an error in Example~2 in 
Sec.~\ref{sec:intro-examples}. However, to detect more complex rules, we will need to use tools like SMT solvers \cite{z3, cvc4}.

\item ConfigC cannot check for anomalies in a value set for one particular keyword. For example,
  setting a parameter, which relates memory in MySQL configuration 
  files, too large can cause exhausting the RAM and causing extreme 
  slowness or even a crash. Such an anomalous value does not violate any
  previously mentioned constraints (such as type errors or ordering errors), but yet 
  it makes system behave wrongly.

@@

This proposal aims to address all the above limitations.
